Validation of marker gene expression

### 2025-02-27 analyses/cell-type-consensus/template-notebooks/marker-gene-validation.Rmd
use is renv project

```{r base paths}
# The base path for the OpenScPCA repository, found by its (hidden) .git directory
repository_base <- rprojroot::find_root(rprojroot::is_git_root)
module_base <- file.path(repository_base, "analyses", "cell-type-consensus")

# path to results directory
results_dir <- file.path(repository_base, "data", "current", "results", "cell-type-consensus", params$project_id)
```

>>>>

```{r base paths}
# The path for this module
module_base <- rprojroot::find_root(rprojroot::is_renv_project)

# path to results directory
results_dir <- file.path(module_base, "..", "..", "data", "current", "results", "cell-type-consensus", params$project_id)
```
